Vertical shear instability in astrophysical disks: vertically global linear calculations with thermal relaxation and applications to the Solar Nebula

### 2015-03-13 numerical.tex
updating

However, the fundamental mode is dominant for $\beta \geq 
0.03$. Higher order modes, with larger growth rates than the
fundamental mode, are more effectively stabilized with increasing 
$\beta$. For $\beta=0.1$, which is close to $\beta_\mathrm{crit}$, we
only find the fundamental mode.

@@

Fig. \ref{lowfreq_eigenfunc_cool}---\ref{lowfreq_eigenfunc_2d_cool}
shows the fundamental mode with $\khat=10$ in a disk with 
$\beta=0.1$. These plots can be compared the case with rapid thermal
relaxation (Fig. \ref{lowfreq_eigenfunc}---\ref{lowfreq_eigenfunc_2d}). We see 
that increasing $\beta$ causes the region characterized by $W\sim z$ and  
$\delta v_z\sim$ constant closer to the mid-plane, with oscillatory
behavior emerging near vertical boundaries where buoyancy becomes
important. This leads to the `tilted' pressure perturbations seen in
Fig. \ref{lowfreq_eigenfunc_2d_cool}
(cf. Fig. \ref{lowfreq_eigenfunc_2d}). However, most of the meridional
momentum is still contained within $|z|\lesssim 2H$ as for 
the case with $\beta=10^{-3}$.

@@

% may need to explain why choose k=10
% bcrit independent of k for k>>1 
% for some parameter regimes (e.g. large q, large epsilon) 
% behavior at larger kx and finite bcool not understood. 
We further test the dependence of the critical thermal relaxation timescale 
$\beta_\mathrm{crit}$ on disk parameters
(Eq. \ref{iso_vsi_cond}).  We use the previous case study as a
reference point and vary $q\in[-0.2,-1.2]$, 
$\gamma\in[1.2,2.0]$, and $\epsilon\in[0.02,0.1]$
separately. Here, we use a wavenumber $\khat=10$, for which we
find growth rates reach zero for the range of disk parameters
considered, so that a numerical $\beta_\mathrm{crit}$ can be defined precisely.

>>>>

However, the fundamental mode is dominant for $\beta \geq 
0.03$. Higher order modes, with larger growth rates than the
fundamental mode, are more effectively stabilized with increasing 
$\beta$.

For $\beta=0.1$, which is close to $\beta_\mathrm{crit}$, we
only find the fundamental mode.

@@

Fig. \ref{lowfreq_eigenfunc_cool}---\ref{lowfreq_eigenfunc_2d_cool}
shows the fundamental mode with $\khat=10$ in a disk with 
$\beta=0.1$. These plots can be compared the case with rapid thermal
relaxation (Fig. \ref{lowfreq_eigenfunc}---\ref{lowfreq_eigenfunc_2d}). We see 
that increasing $\beta$ causes the region characterized by $W\sim z$ and  
$\delta v_z\sim$ constant closer to the mid-plane, with oscillatory
behavior emerging near vertical boundaries where buoyancy becomes
important. This leads to the `tilted' pressure perturbations seen in
Fig. \ref{lowfreq_eigenfunc_2d_cool}
(cf. Fig. \ref{lowfreq_eigenfunc_2d}). % However, most of the meridional
% momentum is still contained within $|z|\lesssim 2H$ as for 
% the case with $\beta=10^{-3}$.

@@

% may need to explain why choose k=10
% bcrit independent of k for k>>1 
% for some parameter regimes (e.g. large q, large epsilon) 
% behavior at larger kx and finite bcool not understood. 
We further test the dependence of the critical thermal relaxation timescale 
$\beta_\mathrm{crit}$ on disk parameters
(Eq. \ref{iso_vsi_cond}).  We use the previous case study as a
reference point and vary $q\in[-0.2,-1.2]$, 
$\gamma\in[1.2,2.0]$, and $\epsilon\in[0.02,0.1]$
separately.%  Here, we use a wavenumber $\khat=10$, for which we
% find growth rates reach zero for the range of disk parameters
% considered, so that a numerical $\beta_\mathrm{crit}$ can be defined precisely.
